An Early Eocene temperature gradient modelled with geological and ecological proxies

### 2022-09-27 manuscript/manuscript.Rmd
title change and model assessment fix

---
title: "The Early Eocene Climate Optimum reconstructed with Bayesian multi-proxy integration"

@@

<!-- discarded titles:
Modelling latitudinal temperature gradients from geological proxies: An early Eocene example
"Improving palaeoclimatic reconstructions with ecological data: How hot was the early Eocene?"
"Integrating ecological and geochemical proxies for palaeoclimatic reconstruction: An early Eocene example"

-->

>>>>

---
title: "An Early Eocene temperature gradient modelled with geological and ecological proxies"

@@

<!-- discarded titles:
Modelling latitudinal temperature gradients from geological proxies: An early Eocene example
"Improving palaeoclimatic reconstructions with ecological data: How hot was the early Eocene?"
"Integrating ecological and geochemical proxies for palaeoclimatic reconstruction: An early Eocene example"
"The Early Eocene Climate Optimum reconstructed with Bayesian multi-proxy integration"
-->
